A hyperdimensional code for sequences and trees inspired by chromosomal crossover

### 2019-09-02 ms/crossing_over.tex
Add seq encoding and decoding algs.

\usepackage{arxiv}
\usepackage{amsmath}

@@

\title{A hyperdimensional sequence code inspired by chromosomal crossover}

@@

\section{Algorithm}

@@

\subsection{Algorithm}

Given a dictionary $D$ of $M$ symbols $s^1, ..., s^M$, we will first sample a "C-basis" (crossover basis) $B$ and an auxiliary mask function $\mu$ from $P(B)$ and $P(\mu)$, respectively. Using $B$ and $\mu$, we will then deterministically build codes $\{X^Y\}$ of arbitrary sequences $\{Y = (y_1, ..., y_L)\}$, where $y_t \in D$.

@@

2. Sample a "mask function" $\mu \sim P(\mu)$, where $\mu:(X^A, X^B) \rightarrow [0, 1]^N$ and is represented by a matrix with $N$ rows and $Z^{2N}$ columns, with i.i.d. real-valued elements from $\textrm{Uniform}(0, 1)$. We reference elements of $\mu$ with the notation $\mu(j, X^A, X^B)$.

In practice $\mu$ need not be sampled explicitly, which would take astronomical time; it suffices to use, say, to map $(X^A, X^B)$ using a hash function like SHA-1 to an integer, then sample $N$ times from $\textrm{Uniform}(0, 1)$ from a random number generator seeded with this integer.

\textbf{Encoding}

...

@@

\section{Comparison to existing hyperdimensional computing codes}

>>>>

\usepackage{arxiv}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

@@

\title{A hyperdimensional code for sequences and trees inspired by chromosomal crossover}

@@

\section{Problem statement}

@@

\section{Sequence encoding}

\textbf{Summary}

Given a dictionary $D$ of $M$ symbols $s^1, ..., s^M$, we first sample a "C-basis" (crossover basis) $B$ and an auxiliary "mask function" $\mu$ from $P(B)$ and $P(\mu)$, respectively. Using $B$ and $\mu$, we will then deterministically build codes $\{X^Y\}$ of arbitrary sequences $\{Y = (y_1, ..., y_L)\}$, where $y_t \in D$.

@@

2. Sample a "mask function" $\mu \sim P(\mu)$, where $\mu:(X^A, X^B) \rightarrow [0, 1]^N$ and is represented by a matrix with $N$ rows and $Z^{2N}$ columns, with i.i.d. real-valued elements from $\textrm{Uniform}(0, 1)$. We reference elements of $\mu$ with the notation $\mu(j, X^A, X^B)$. (In practice $\mu$ need not be sampled explicitly, which would take astronomical time; it suffices to use, say, to map $(X^A, X^B)$ using a hash function like SHA-1 to an integer, then sample $N$ times from $\textrm{Uniform}(0, 1)$ from a random number generator seeded with this integer.)

\begin{algorithm}
\caption{Sequence Encoding}

\begin{algorithmic}[0]
\Function{EncodeSequence}{$Y; B, \mu$}
\State $X^Y \gets X^*$
\For{$t \in 1, ..., |Y|$}

\State $X^Y[\mu(:, X^Y, X^{y_t}) < 1/(t+1)^\gamma] \gets X^{y_t}[\mu(:, X^Y, X^{y_t}) < 1/(t+1)^\gamma]$

\EndFor

\State \textbf{return} $X^Y$
\EndFunction

\end{algorithmic}
\end{algorithm}

@@

\section{Sequence decoding}
How to decode a sequence

\begin{algorithm}
\caption{Sequence Decoding}

\begin{algorithmic}[0]
\Function{DecodeSequence}{$X^Y; B, \mu$}
\State $\hat{X}^Y \gets X^*$
\State $d \gets \textrm{Hamming}(\hat{X}^Y , X^*)$
\State $t = 1$

\While{$d > 0$}

\State $(i_{best}, \hat{X}^Y_{best}, d_{best}) \gets (Null, Null, 1)$

    \For{$i \in 1, ..., M$}

        \State $\hat{X}^Y_{temp} \gets \hat{X}^Y $
        \State $\hat{X}^Y_{temp}[\mu(:, \hat{X}^Y, X^i) < 1/(t+1)^\gamma] \gets X^i[\mu(:, \hat{X}^Y, X^i) < 1/(t+1)^\gamma]$
        \State $d_{temp} \gets \textrm{Hamming}(X^Y, \hat{X}^Y_{temp})$

        \If{$d_{temp} < d_{best}$}

            \State $(i_{best}, \hat{X}^Y_{best}, d_{best}) \gets (i, \hat{X}^Y_{temp}, d_{temp})$

        \EndIf
    \EndFor

    \If{$d_{best}\geq d$}

        \State \textbf{return} $y_1, ..., y_t$

    \Else

        \State $(y_t, \hat{X}^Y, d) \gets (i_{best}, \hat{X}^Y_{best}, d_{best})$
        \State $t = t+1$

    \EndIf

\EndWhile

\State \textbf{return} $y_1, ..., y_t$
\EndFunction

\end{algorithmic}
\end{algorithm}

\section{Improving decoding with $\gamma$}

\section{Trees}

\begin{algorithm}
\caption{Tree Encoding}

\begin{algorithmic}[0]
\Function{EncodeTree}{$T; B, \mu$}

\State $D^T \gets \{i: X^i \textrm{ \textbf{for} } i \in 1, ..., M\}$

\For{$J \in T$}

    \State $X^T \gets D^T[J_1]$
    \For{$k \in 2, ..., |J|$}
        \State $mask \gets k/|J| \leq \mu(:, J) \leq (k+1)/|J|$
        \State $X^T[mask] \gets J_k[mask]$
    \EndFor

    \State $D^T[J] \gets X^T$
\EndFor

\State \textbf{return} $D^T[T[end]]$
\EndFunction

\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Tree Decoding}

\begin{algorithmic}[0]
\Function{DecodeTree}{$Y; B, \mu$}
\State $X^Y \gets X^*$
\For{$t \in 1, ..., \textrm{len}(Y)$}

\State $X^Y[\mu(:, X^Y, X^{y_t}) < 1/(t+1)^\gamma] \gets X^{y_t}[\mu(:, X^Y, X^{y_t}) < 1/(t+1)^\gamma]$

\EndFor

\State \textbf{return} $X^Y$
\EndFunction

\end{algorithmic}
\end{algorithm}

\section{Mask correlations}

\section{Discussion}
